---
title: "Strategic Decision Making in the 3D Printing Industry - A Robust Decision Making (RDM) analysis"
author: "Pedro Nascimento de Lima"
date: "25 de setembro de 2018"
output: 
  beamer_presentation:
    theme: Berlin 
    slide_level: 3
    toc: true
# "Darmstadt"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Why 3D Printing

### Key Features of 3D printing

 - 3D printing may

### Why 3D Printing?

3D Printing is an emergint technology, but decision makers face uncertainty.

#### Positive Evidence
 - 3D printing Industry has seen two digits growth consistently in the last few years;
 - 3D printing is already reshaping supply chains across industries (e.g.: prothesis, aerospace, etc.);

#### Negative Evidence
 - Major players have been observing declining profitability (e.g.: Stratasys, 3D Systems);
 - Estimates of 3D printing growth diverge;

### 3D Printing Prospected Effects - Why do we Care?


### Shaping events in the 3D Printing Industry

A confluence of events are

#### Patent Dynamics and Expiration
The FDM patent expiration in 2007


#### Strategies Played by Key Players
Leading 3D printing players (e.g. 3D Systems and Stratasys) historically have been adopting a closed-source strategy.

However, the key event leading to 3D printing growth was patent expiration.

##### Dynamyc Hipothesis 1: Holding Patents m


#### A fourth level

Some Text Here

##### A fith level

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

# XLRM

## Model

```{r cars, echo = TRUE}
summary(cars)
```

# Case Generation

# Scenario Discovery

# Tradeoffs

# Second Iteration

# Final Thoughts

## Slide with Plot

```{r pressure}
plot(pressure)
```

