---
title: "Strategic Decision Making in the 3D Printing Industry - A Robust Decision Making (RDM) analysis"
author: "Pedro Nascimento de Lima"
date: "25 de setembro de 2018"
output: 
  beamer_presentation:
    theme: Berlin 
    slide_level: 3
    toc: true
fig_width: 9 
fig_height: 4 


# "Darmstadt"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
library(DT)
```

# Why 3D Printing

### Key Features of 3D printing

 - 3D printing may

### Why 3D Printing?

3D Printing is an emergint technology, but decision makers face uncertainty.

#### Positive Evidence
 - 3D printing Industry has seen two digits growth consistently in the last few years;
 - 3D printing is already reshaping supply chains across industries (e.g.: prothesis, aerospace, etc.);

#### Negative Evidence
 - Major players have been observing declining profitability (e.g.: Stratasys, 3D Systems);
 - Estimates of 3D printing growth diverge;

### 3D Printing Prospected Effects - Why do we Care?


### Shaping events in the 3D Printing Industry

- Patent Dynamics

#### Patent Dynamics and Expiration
The FDM patent expiration in 2007


#### Strategies Played by Key Players
Leading 3D printing players (e.g. 3D Systems and Stratasys) historically have been adopting a closed-source strategy.

However, the key event leading to 3D printing growth was patent expiration.

##### Dynamyc Hipothesis 1: Holding Patents m


#### A fourth level

Some Text Here

##### A fith level

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

# XLRM

## Model

```{r cars, echo = TRUE}
summary(cars)
```

# Case Generation

### Design of Experiments

- Full factorial design of these variables, resulting in 54 strategies:

|Variable | Meaning | Levels |
|-----------|---------------------------------------|------------------------|
| $S_1$ | Market & Pricing Strategy. Defines wether the player pursue an agressive marketing strategy to gain market share (by cutting prices and accepting excess capacity), or pursue a conservative strategy, | Agressive (1); Conservative (2)|
| $S_1^{max}$ or $S_1^{min}$ | Desired Market Share. For a Conservative Strategy, the player adopts the $S_1^{max}$, and for an Agressive Strategy, $S_1^{min}$ | 20%; 30%; 40%|
| $\eta_1$ | R & D budget, as a fraction of revenue. | 5%; 10%; 15%|
| $\kappa_i$ | Fraction of R & D budget released to open source technologies. | 0 %; 50 %; 90 % |


### Candidate Strategy NPV across scenarios

```{r, fig.align='center'}
plots_results$plots_linha_geral$plot_estrategia_candidata_vpl
```

### Global Demand across scenarios

```{r, fig.align='center'}
plots_results$plots_linha_geral$plot_estrategia_candidata_demanda_global
```

### Market Share of the 4 Players in a given scenario

```{r, fig.align='center'}
plots_results$plots_players$plot_players_vpl
```


### Net Present Value across strategies and Scenarios

```{r, fig.align='center'}
plots_results$plots_whisker$plot_whisker_lever_profit
```

### Regret across strategies and Scenarios

```{r, fig.align='center'}
plots_results$plots_whisker$plot_whisker_lever_regret
```

### Ranking Strategies by Regret

```{r}

formatted_strategies_ranking = ranking_estrategias[,c(1, 6, 8, 9, 7, 3)]


# Parei aqui

formatted_strategies_ranking[,c(3,4,5)] = format_for_humans(formatted_strategies_ranking[,3])

# Não dá para usar isso.
# formatted_strategies_ranking = DT::datatable(formatted_strategies_ranking) %>% 
#   DT::formatCurrency(columns = 5, digits = 0) %>%
#   DT::formatPercentage(columns = c(2:4), digits = 0)

column_names = c("Lever", "Capac. Strategy", "Desired Mkt Share", "R&D Inv.", "Open Source R&D", "Profit Regret 75% percentile")

knitr::kable(x = head(formatted_strategies_ranking, 10), col.names = column_names, digits = 2, format="latex", booktabs=TRUE) %>% 
  kable_styling(latex_options="scale_down")

```


# Scenario Discovery

# Tradeoffs

# Second Iteration

# Final Thoughts

## Slide with Plot

```{r pressure}
plot(pressure)
```

