---
title: "PlotsTest"
author: "Pedro Nascimento de Lima"
date: "10/11/2018"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
results_path = "C:/Temporario/rdm-results-backup/"
if (!exists(x = "plots_results")){
 load(paste0(results_path,"plots_results.rda")) 
}
```

## Candidate Strategy NPV across scenarios

```{r}
plots_results$plots_linha_geral$plot_estrategia_candidata_vpl
```

## Candidate Strategy NPV across scenarios

```{r}
plots_results$plots_linha_geral$plot_estrategia_candidata_vpl
```

## Global Demand across scenarios

```{r, fig.align='center',fig.height=2.8,fig.width=4.5}
plots_results$plots_linha_geral$plot_estrategia_candidata_demanda_global
```

## Previous Image

\centerline{\includegraphics[height=2.5in]{images/npv.png}}

## Global Demand across scenarios

\centerline{\includegraphics[height=2.5in]{images/sales.png}}

## 4 Players Net Present Value in a given scenario

\centerline{\includegraphics[height=2.5in]{images/npv-players.png}}

## Net Present Value across strategies and Scenarios

\centerline{\includegraphics[height=2.5in]{images/npv-whisker.png}}

## Regret across strategies and Scenarios

\centerline{\includegraphics[height=2.5in]{images/regret-whisker.png}}